---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# strapr

<!-- badges: start -->

<!-- badges: end -->

## Summary

Performs bootstrapping of a dataset column to produce plots and statistics for use in final reports and documents.

The purpose of this package is to simplify and automate the process of creating simple bootstrap distributions of numerical data columns. The package will have a module which intakes a dataset column and relevant parameters such as the desired confidence bounds and number of simulations. The module will perform the simulation statistics to generate the bootstrap mean distribution and relevant statistics such as the sample mean and bootstrapped confidence interval. The package will also contain a module for visualization of the bootstraped confidence interval, and a module for creating a professional publication-ready table of the relevant statistics.

## **Package context within the R ecosystem**

The package builds conceptually on the [infer package](https://cran.r-project.org/web/packages/infer/index.html) and the [boot package](https://cran.r-project.org/web/packages/boot/), which allows one to conduct the bootstrap sampling using the generate() and boot() functions. strapr will streamline and extend this process from the pure statistical process done in these modules. The [BootCI](https://rdrr.io/cran/DescTools/man/BootCI.html) package seems to streamline the confidence interval process but does not include plotting support. While we cannot be certain that one does not exist, there does not seem to be a package which streamlines the process from data to visualization and presentation as proposed in this document. Some tutorials on bootstrap confidence intervals at <https://moderndive.com/8-confidence-intervals.html>, <http://pages.stat.wisc.edu/~larget/stat302/chap3.pdf> and <https://www.geeksforgeeks.org/bootstrap-confidence-interval-with-r-programming/> encourage the reader to plot the results manually.

## Installation

You can install the released version of strapr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("strapr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/strapr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library("strapR")
# plot_ci([1, 2, 3, 4, 5, 6, 7], 1000, n = 100, ci_level = 0.95, ci_random_seed = 123)
```

## Function Usage

-   bootstrap_distribution: A sampling distribution of \`rep\` replicates is generated for a specified estimator with replacement for a given bootstrap sample size.

-   calculate_boot_stats: A confidence interval for a given sampling distribution is calculated for a given confidence level. The interval and other statistics relevant to the distribution and its creation are returned in a dictionary.

-   plot_ci: Plots a bootstrapped sampling distribution with its confidence interval and observed mean.

-   tabulate_stats: Generates two tables contains the sampling distribution's statistics and the parameters of the bootstrapping method.

## Contributing

Julien Gordon, Gautham Pughazhendhi, Zack Tang, and Margot Vore.

## License

\`strapr\` was created by Julien Gordon, Gautham Pughazhendhi, Zack Tang, Margot Vore. It is licensed under the terms of the MIT license.
